### 2021-03-15 treatise-context/2_problem_setting.tex
Chap 4: double check grammar

We consider the hybrid beamforming at both transmitter and receiver ends, as shown in Figure 2.
Each end consists of both digital and analog precoders and combiners.
In the transmitter end, there are (seeing towards the receiver end), digital precoder \m {\M {F} _B \in \MB {C} ^{N_{B,t} \D N_{B,t}}} and analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_{B,t}}}.
Similarly, in the receiver end, there are (seeing towards the transmitter end) digital combiner \m {\M {W} _R \in \MB {C} ^{N_{B,r} \D N_H}} and analog combiner \m {\M {W} _B \in \MB {C} ^{N_{B,r} \D  N_{B,r}}}.

Recall that analog precoders may only have values of unity magnitude,
%
\DispNum {F:R:1::R1} {
\NC \Nm {\RB {\M {F} _R} _{\SB {n_H, n_{R,t}}}}
= \NC 1, \NR
%
\NC \Nm {\RB {\M {W} _R} _{\SB {n_{R,r}, n_H}}}
= \NC 1, \NR
%
\NC n_H
= \NC 0, \dots N_H-1, \NR
%
\NC n_{R,t}
= \NC 0, \dots N_{B,t}-1 \NR
%
\NC n_{R,r}
= \NC 0, \dots N_{B,r}-1 \NR
}
%
And we assume
%
\DispNum {N:H:NY:NY} {
\NC N_H \gg \NC N_{B,t}, N_{R,t} \NR
}

>>>>

We consider hybrid beamforming at both the transmitter and receiver ends, as shown in Figure 2.
Each end consists of both digital and analog precoders and combiners.
In the transmitter end, there are (seeing towards the receiver end), the digital precoder \m {\M {F} _B \in \MB {C} ^{N_{B,t} \D N_{B,t}}} and the analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_{B,t}}}.
Similarly, in the receiver end, there are (seeing towards the transmitter end) the digital combiner \m {\M {W} _B \in \MB {C} ^{N_{B,r} \D  N_{B,r}}} and the analog combiner \m {\M {W} _R \in \MB {C} ^{N_{B,r} \D N_H}}.

Recall that analog precoders may only have values of unity magnitude,
%
\DispNum {F:R:1::R1} {
\NC \Nm {\RB {\M {F} _R} _{\SB {n_H, n_{R,t}}}}
= \NC 1, \NR
%
\NC \Nm {\RB {\M {W} _R} _{\SB {n_{R,r}, n_H}}}
= \NC 1, \NR
%
\NC n_H
= \NC 0, \dots N_H-1, \NR
%
\NC n_{R,t}
= \NC 0, \dots N_{B,t}-1 \NR
%
\NC n_{R,r}
= \NC 0, \dots N_{B,r}-1 \NR
}
%
And we assume
%
\DispNum {N:H:NY:NY} {
\NC N_H \gg \NC N_{B,t}, N_{B,r} \NR
}

### 2021-03-15 treatise-context/3_2_generating_beamforming_matrices.tex
Chap 4: double check grammar

In Haviv and Regev, \quotation {The restricted isometry property of subsampled Fourier matrices} \cite [KlM17], Theorem \m {4.5} states a DFT submatrix has \m {\d_s} RIP with failure probability lower than a certain Big-O bound.
We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_H s} RIP .
In conclusion, (respectively for \m {N_{B,r}})
%
\DispNum {N:R:sd':NH} {
\NC N_{B,t}
\geq \NC \F {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \NR
}
%
Drop \m {\log \SB {1 /\d_s}^2} and the denominator \m {\d_s} in \m {\log \SB {s /\d_s}^2} in \Rf {N:R:sd':NH}, to get the statement below.

>>>>

In Haviv and Regev, \quotation {The restricted isometry property of subsampled Fourier matrices} \cite [KlM17], Theorem \m {4.5} states a big O bound for the failure probability of a DFT submatrix with \m {\d_s} RIP.
We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_H s} RIP.
In conclusion, (respectively for \m {N_{B,r}})
%
\DispNum {N:R:sd':NH} {
\NC N_{B,t}
\geq \NC \F {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \NR
}
%
Drop \m {\log \SB {1 /\d_s}^2} and the denominator \m {\d_s} in \m {\log \SB {s /\d_s}^2} in \Rf {N:R:sd':NH}, to get the statement below.

### 2021-03-15 treatise-context/4_simulation.tex
Slightly correct grammar
Chap 4: double check grammar

Let us represent complex vector and matrices by real vector and matrices.
For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MS {R} \SB {\V {x}}} of \m {\V {x}} to be
%
\DispNum {R:x:R2:M1} {
\NC \MS {R} \SB {\V {x}}
\in \NC \MB {R} ^{2M} \NR
\NC \MS {R} \SB {\V {x}} _{\SB {m}}
= \NC \startcases
\NC \MF {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \NR
\NC \MF {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \NR
\stopcases \NR
\NC m' 
= \NC  0, 1, 2, \ldots, M-1 \NR
}
%
The injection is obvious, and we may define \m {\MS {R} ^{-1}} so that
%
\DispNum {R:1:x::x:} {
\NC \MS {R} ^{-1} \SB {\MS {R} \SB {\V {x}}}
=\NC \V {x} \NR
}
%
Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
For \m {\M {A} \in \MB {C} ^{M_1 \D M_2}}, define real representation \m {\MS {R} \SB {\M {A}}} of \m {\M {A}} to be
%
\DispNum {R:A:R2:21} {
\NC \MS {R} \SB {\M {A}}
\in \NC \MB {R} ^{2M_1 \D 2M_2} \NR
\NC \MS {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
\NC \startcases
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \NR
\NC \MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \NR
\NC -\MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \NR
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \NR
\stopcases \NR
\NC m_1 
= \NC 0, 1, 2, \ldots, M_1 -1 \NR
\NC m_2 
= \NC 0, 1, 2, \ldots, M_2 -1 \NR
}

@@

If more than one stage of estimation is possible, that is, there are more than one data sets, the second stage may be run on the second dataset, and so on.
It is possible in theory to run it for three or more times.

@@

However, there is not simple way to determine the value of \m {\l} in advance.
We have tried basis pursuit denoising, with \m {\l = N_H^2 / \g_{\Rm {DS}}} in the simulation.

@@

Denote the threshold for DS to be \m {\g_{\Rm {DS}}}, and similar threshold of Lasso to be \m {\g_{\Rm {Lasso}}}.
We set \m {\g_{\Rm {DS}} = 2 \R {\log N_H}} as suggested in \cite [CaT07].
For sake of comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
For OMP, we consult Cai and Wang \cite [CaW11] for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
We take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\Rm {OMP}} = \R {3} \SB {N_{B,r} N_{B,t}} ^ {1/4}} for 2-norm condition.
Particularly, in the plots of DS only or OMP only, we vary the values of \m {\g_{\Rm {DS}}} and \m {\h_{\Rm {OMP}}} by powers of \m {2}, to observe the effects of thresholds.
The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 \R {N_{B,r} N_{B,t}}}.

@@

In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 6} over \m {N_{B,t}} and \m {N_{B,t}}.
%
\blank [big]
\externalfigure [error-small-square-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-small-tall-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-small-wide-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-small-square-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
%
\blank [big]
\externalfigure [error-small-tall-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
%
\blank [big]
\externalfigure [error-small-wide-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {4} stages, error.}

@@

In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 12} over \m {N_{B,t}} and \m {N_{B,t}}.
%
\blank [big]
\externalfigure [error-medium-square-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-medium-tall-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-medium-wide-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 4, N_H = 12}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-medium-square-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
%
\blank [big]
\externalfigure [error-medium-tall-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
%
\blank [big]
\externalfigure [error-medium-wide-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 4, N_H = 12}, with \m {4} stages, error.}

@@

In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 18} over \m {N_{B,t}} and \m {N_{B,t}}.
%
\blank [big]
\externalfigure [error-big-square-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-big-tall-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 9, N_H = 18}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-big-wide-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 6, N_H = 18}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-big-square-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, with \m {4} stages, error.}
%
\blank [big]
\externalfigure [error-big-tall-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 9, N_H = 18}, with \m {4} stages, error.}
%
\blank [big]
\externalfigure [error-big-wide-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 6, N_H = 18}, with \m {4} stages, error.}

@@

For Lasso, \m {\g} (or \m {\l}) is also crucial to the performance, but cannot be obtained in advance.
Thus, for sake of comparison, we set the same threshold (and BPDN) for Lasso and DS.
Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.

@@

Suppose a linear program has \m {N} dimension variable and \m {M} inequality constraints, then the complexity is \m {\MS {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite [BoV04], p.6).
For our case, that would be \m {\MS {O} \SB {4 N_H ^4 \D 8 N_H^2} = \MS {O} \SB {N_H^6}}.
But other algorithms exist, where, in general, complexity of convex programs is difficult to analyze, as it is not easily to determine how many steps were calculated.

@@

Simulation illustrates that \m {t_{\Rm {DS}}} grows tremendously with \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite [FrS07] on the high complexity of DS.
It is not surprising, regarding the fact that the convex program has to find the Newton step by calculating \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
The matrix inversion is probably the bottleneck of complexity.
However, as we noted above, that different tolerance level of and maximal iteration number may result in vastly different computation time.

>>>>

Let us represent complex vectors and matrices by real vectors and matrices.
For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MS {R} \SB {\V {x}}} of \m {\V {x}} to be
%
\DispNum {R:x:R2:M1} {
\NC \MS {R} \SB {\V {x}}
\in \NC \MB {R} ^{2M} \NR
\NC \MS {R} \SB {\V {x}} _{\SB {m}}
= \NC \startcases
\NC \MF {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \NR
\NC \MF {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \NR
\stopcases \NR
\NC m' 
= \NC  0, 1, 2, \ldots, M-1 \NR
}
%
The injection is obvious, and we may define \m {\MS {R} ^{-1}} so that
%
\DispNum {R:1:x::x:} {
\NC \MS {R} ^{-1} \SB {\MS {R} \SB {\V {x}}}
=\NC \V {x} \NR
}
%
Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
For \m {\M {A} \in \MB {C} ^{M_1 \D M_2}}, define real representation \m {\MS {R} \SB {\M {A}}} of \m {\M {A}} to be
%
\DispNum {R:A:R2:21} {
\NC \MS {R} \SB {\M {A}}
\in \NC \MB {R} ^{2M_1 \D 2M_2} \NR
\NC \MS {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
\NC \startcases
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \NR
\NC \MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \NR
\NC -\MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \NR
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \NR
\stopcases \NR
\NC m_1 
= \NC 0, 1, 2, \ldots, M_1 -1 \NR
\NC m_2 
= \NC 0, 1, 2, \ldots, M_2 -1 \NR
}

@@

If more than one stage of estimation is possible, that is, there are more than one dataset, the second stage may be run on the second dataset, and so on.
It is possible in theory to run it for three or more times.

@@

However, there is no simple way to determine the value of \m {\l} in advance.
We have tried basis pursuit denoising, with \m {\l = N_H^2 / \g_{\Rm {DS}}} in the simulation.

@@

Denote the threshold for DS to be \m {\g_{\Rm {DS}}}, and similar threshold of Lasso to be \m {\g_{\Rm {Lasso}}}.
We set \m {\g_{\Rm {DS}} = 2 \R {\log N_H}} as suggested in \cite [CaT07].
For sake of comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
For OMP, we consult Cai and Wang \cite [CaW11] for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
We take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\Rm {OMP}} = \R {3} \RB {N_{B,r} N_{B,t}} ^ {1/4}} for 2-norm condition.
The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 \R {N_{B,r} N_{B,t}}}.

@@

In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 6} over \m {N_{B,t}} and \m {N_{B,r}}.
%
\blank [big]
\externalfigure [error-small-square-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-small-tall-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-small-wide-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-small-square-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
%
\blank [big]
\externalfigure [error-small-tall-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
%
\blank [big]
\externalfigure [error-small-wide-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {4} stages, error.}

@@

In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 12} over \m {N_{B,t}} and \m {N_{B,r}}.
%
\blank [big]
\externalfigure [error-medium-square-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-medium-tall-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-medium-wide-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 4, N_H = 12}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-medium-square-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
%
\blank [big]
\externalfigure [error-medium-tall-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
%
\blank [big]
\externalfigure [error-medium-wide-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 4, N_H = 12}, with \m {4} stages, error.}

@@

In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 18} over \m {N_{B,t}} and \m {N_{B,r}}.
%
\blank [big]
\externalfigure [error-big-square-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-big-tall-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 9, N_H = 18}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-big-wide-two.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 6, N_H = 18}, with \m {2} stages, error.}
%
\blank [big]
\externalfigure [error-big-square-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, with \m {4} stages, error.}
%
\blank [big]
\externalfigure [error-big-tall-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 9, N_H = 18}, with \m {4} stages, error.}
%
\blank [big]
\externalfigure [error-big-wide-four.png] [wfactor=fit, hfactor=fit]
\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 6, N_H = 18}, with \m {4} stages, error.}

@@

For Lasso, \m {\g} (or \m {\l}) is also crucial to the performance, but cannot be obtained in advance.
Thus, for sake of comparison, we set the same threshold for Lasso and DS.
Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.

@@

Suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\MS {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite [BoV04], p.6).
For our case, that would be \m {\MS {O} \SB {4 N_H ^4 \D 8 N_H^2} = \MS {O} \SB {N_H^6}}.
But other algorithms exist, where, in general, complexity of convex programs is difficult to analyze, as it is not easily to determine how many steps were calculated.

@@

Simulation illustrates that \m {t_{\Rm {DS}}} grows tremendously with \m {N_H}, agreeing Friedlander and Saunders \cite {FrS07} who noted the high complexity of DS.
This is not surprising, since the inversion of \m {\M {P} \M {P} ^\Adj} is probably the bottleneck of complexity, which has dimension \m {\M {N}_H^2}.
By the way, different tolerance levels and maximal iteration numbers may result in vastly different computation time.

### 2021-03-15 treatise-context/5_conclusion.tex
Chap 4: double check grammar

The treatise aims to answer the problem of effective estimating a MIMO millimeter-wave channel by exploiting its sparsity.
To do so, we try the Dantzig Selector (DS) for channel estimation.
We exploited the sparsity in the spatial frequency domain, and justified the RIP of effective beamforming matrix for the hybrid structure.
We then proved quantitatively that the expected error norm is bounded for overwhelming probability.
We also suggested several ways to reduce the complexity without losing much performance, as justified by simulation.
Simulation is done, and we see that DS indeed outperforms other methods.

We corroborate the prediction that DS is nearly optimal, and it may extract more information than other methods do when the sampling rate is low.
When the sample is less abundant and the noise level is higher, sometimes only DS can recover successfully.
Therefore, one may use DS in the scenario that precision is crucial, as well as that the number of RF chains is more limited or fewer stages of estimation is possible.

>>>>

The treatise aims to answer the problem of effective estimating a MIMO mm-wave channel by exploiting its sparsity.
To do so, we apply the Dantzig Selector (DS), by exploiting the sparsity in the spatial frequency domain, and justified the restricted isometry of the effective beamforming matrix.
We then prove quantitatively that the expected error norm is bounded for overwhelming probability.
We also suggest several ways of reducing the complexity without losing much performance.
Simulation is done, and we see that DS indeed outperforms other methods in most datasets.

We corroborate the prediction that DS is nearly optimal, and it may extract more information than other methods do when the sampling rate is low.
When the sample is less abundant and the noise level is higher, sometimes only DS can recover successfully.
Therefore, one may use DS in the scenario that precision is crucial, as well as the case that the number of RF chains is more limited or fewer stages of estimation are possible.

### 2021-03-15 treatise-pdflatex/2_problem_setting.tex
Chap 4: double check grammar

We consider the hybrid beamforming at both transmitter and receiver ends, as shown in Figure 2.
Each end consists of both digital and analog precoders and combiners.
In the transmitter end, there are (seeing towards the receiver end), digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_{B,t} \D N_{B,t}}} and analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_H \D N_{B,t}}}.
Similarly, in the receiver end, there are (seeing towards the transmitter end) digital combiner \m {\M {W} _R \in \mathbb {C} ^{N_{B,r} \D N_H}} and analog combiner \m {\M {W} _B \in \mathbb {C} ^{N_{B,r} \D N_{B,r}}}.

>>>>

We consider hybrid beamforming at both the transmitter and receiver ends, as shown in Figure 2.
Each end consists of both digital and analog precoders and combiners.
In the transmitter end, there are (seeing towards the receiver end), the digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_{B,t} \D N_{B,t}}} and the analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_H \D N_{B,t}}}.
Similarly, in the receiver end, there are (seeing towards the transmitter end) the digital combiner \m {\M {W} _B \in \mathbb {C} ^{N_{B,r} \D N_{B,r}}} and the analog combiner \m {\M {W} _R \in \mathbb {C} ^{N_{B,r} \D N_H}}.

### 2021-03-15 treatise-pdflatex/3_2_generating_beamforming_matrices.tex
Chap 4: double check grammar

In Haviv and Regev, ``The restricted isometry property of subsampled Fourier matrices'' \cite {KlM17}, Theorem \m {4.5} states a DFT submatrix has \m {\d_s} RIP with failure probability lower than a certain Big-O bound.
We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_H s} RIP.
%
\DispNum {N:R:sd':NH} {
N_R
\geq \frac {s} {\d_s^2} \RB {\log \frac{1}{\d_s}}^2 \RB {\log \frac{s}{\d_s}}^2 \log N_H 
}
%
Drop \m {\log \SB {1 /\d_s}^2} and the denominator \m {\d_s} in \m {\log \SB {s /\d_s}^2} in \eqref {N:R:sd':NH}, to get the statement below.

>>>>

In Haviv and Regev, ``The restricted isometry property of subsampled Fourier matrices'' \cite {KlM17}, Theorem \m {4.5} states a big O bound for the failure probability of a DFT submatrix with \m {\d_s} RIP.
We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_H s} RIP.
In conclusion, (respectively for \m {N_{B,r}})
%
\DispNum {N:R:sd':NH} {
N_R
\geq \frac {s} {\d_s^2} \RB {\log \frac{1}{\d_s}}^2 \RB {\log \frac{s}{\d_s}}^2 \log N_H 
}
%
Drop \m {\log \SB {1 /\d_s}^2} and the denominator \m {\d_s} in \m {\log \SB {s /\d_s}^2} in \eqref {N:R:sd':NH}, to get the statement below.
